Describing the scale and composition of police demand in Detroit.

### 2021-08-22 paper.Rmd
paper start

---
title: "Paper summary: police demand and persons with mental ill-health"
output: html_document
tags:
- demand
- reactive demand
- mental health
- calls for service
- text mining
date: '2021-28-04'
---

@@

The question which follows is then: how can we measure police demand? Are we measuring it reliabily

## Mental health

In a recent paper published in _Policing: A Journal of Policy and Practice_, we focused on describing

Police contact with persons experiencing mental ill-health might be the most salient example of these challenges.

 Inevitably, this is not straightforward.

## Mental health

Since my article in The Conversation, I have become increasingly intrigued by the complexities of understanding and measuring police demand. This has largely driven by some of the amazing research that has been published in recent years (see readings below).

In many countries, one such demand type is particularly concerning; those originating from incidents involving people with mental ill-health. In England and Wales, forces have reported that around 2% of incidents relate to mental health, but this is widely understood to be an **underestimate** due to inconsistencies in how incidents are flagged. Not only this, but the proportion of emergency calls for service does not necessarily reflect the **time** police actually consume dealing with such incidents.

These two issues represented a key motivation for the study. We sought to (1) provide an improved, data-driven estimate of the proportion of calls for service involving mental ill-health, and (2) estimate the amount of time officers spend resolving such incidents.

>>>>

---
title: "Describing the scale and composition of police demand in Detroit."
output: pdf_document
header-includes:
  - \usepackage{lscape}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, comment=F, warning=F)
```

@@

\newpage

\begin{landscape}

```{r fig1, fig.align = "center", fig.cap = "Proportional breakdown of deployed time spent on each incident category."}
knitr::include_graphics("visuals/fig1_time_ann.png")
```

\end{landscape}

\newpage

```{r fig2, fig.align = "center", fig.cap = "Mean incident counts by day and week by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig2_time_heat.png")
```

```{r fig3, fig.align = "center", fig.cap = "Spatial patterning of total incident counts by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig3_maps.png")
```
